Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-11 paper/ms.tex
tic 3006 appendix improvements

Figures~\ref{fig:tic3006river} and~\ref{fig:tic3006timegroups} show 120-second
cadence data for TIC~300651846, a CQV in the TESS continuous viewing zone.
With the exception of a few sectors, TESS data will exist for this source
over Sectors 1-12, 27-39, and 61-69.
The majority are in the full frame images, and are the subject of future work.

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{TIC_300651846_P8.254_2min_phase_timegroups.png}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf Orbit-phased plots of TIC 300651846}.
		The envelope has not been subtracted.
	}
	\label{fig:tic3006timegroups}
\end{figure*}

>>>>

Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
120-second cadence data for TIC~300651846, a CQV in the TESS
continuous viewing zone.  If it were not for the existence of
TIC~402980664, this source would likely have been the subject of
greater attention.  With the exception of a few sectors, TESS data
will exist for TIC~300651846 over Sectors 1-12, 27-39, and 61-69.
While most of the available data will exist in the full frame images,
in Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river}
focus only on the 120-second cadence data.

During Sectors 32-39, the source shows between one and four local
minima per cycle.  During the early portions of Sectors 61-65, it is
somewhat more complex, with at least five clear local minima per
cycle.  As the source evolves, this complexity decreases, while the
sharpness of one of the minima appears to increase.  We did not find
evidence for any obvious ``state-switches'' analogous to those that we
observed in LP 12-502; gradual evolution over timescales of
$\approx$50-100 cycles seem to be the norm for TIC~300651846.

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{f11a.pdf}
			\includegraphics[width=0.43\textwidth]{f11b.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf Long-term evolution of TIC 300651846}.
    All available 120-second cadence data as of 11 August 2023 are shown.
    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
    a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
    both panels.
    Light curve segments are split based on the presence of gaps
    longer than three hours.
	}
	\label{fig:tic3006timegroups}
\end{figure*}

@@
